# Synthesis

## Create a summary graph

In the Analysis section, I ran 28 models, each with four parameters.
That makes it hard to get an overview of general trends and differences.
Here, I try to visually present those findings and produce a figure that gives a nice overview.

First, I'll extract all model parameters from the models.
Each one is quite large, so loading them all at once will make my RAM explode.
Instead, I'll iterate over each model:

1. Load the model
2. Extract the estimates
3. Wrangle and relabel them
4. Remove model from workspace again

The below took about a couple of minutes on my laptop.
```{r get-estimates-function, message=FALSE, cache=TRUE}
# get all model names
well_being_indicators <- c("affect", "life")

media <-
  c(
    "music",
    "films",
    "tv",
    "games",
    "books",
    "magazines",
    "audiobooks"
  )

models1 <- 
  paste(rep(well_being_indicators, each = length(media)), media, sep = "_")

models2 <- 
  paste(rep(media, each = length(well_being_indicators)), well_being_indicators, sep = "_")

models <- c(models1, models2)

get_model_estimates <- 
  function(
    models
  ){
    # set up the data set
    estimates <- 
      tibble(
        Predictor = character(),
        Outcome = character(),
        `Use vs. Time` = character(),
        `Between vs. Within` = character(),
        Estimate = double(),
        `Lower CI` = double(),
        `Upper CI` = double()
      )
    
    for (model_name in models) {
      # super lame progress bar
      print(
        paste0(
          "Currently working on: ",
          model_name,
          ". Progress: ",
          which(models==model_name),
          "/",
          length(models)
        )
      )
      # load model
      m <- read_rds(here("models", paste0(model_name, ".rds")))
      
      # get predictor in this model
      predictor <- 
        str_remove(model_name, "_.*") # only take what's before the underscore
      
      # first we get the fixed effects
      dat <- 
        # get fixed effects
        fixef(m) %>% 
        # turn into a tibble and keep rownames because they are the parameter names
        as_tibble(., rownames = "Effect") %>% 
        # outcome will be the second part of the model name after the underscore
        mutate(
          Outcome = model_name,
          Outcome = str_remove(Outcome, ".*_")
        ) %>% 
        # no need for intercept parameters
        filter(!str_detect(Effect, "Intercept"))
      
      # if statement to see how to rename model estimates
      if (predictor %in% c("affect", "life")){
        dat <- 
          dat %>% 
          # we need to rename the parameters so that their patterns fit with a model that has a media predictor
          mutate(
            # life_satisfaction adds an extra underscore which breaks the rest of the code below, so I'll just replace it here (if it's affect, it won't matter)
            Effect = str_replace(Effect, "life_satisfaction", "life"),
            Effect = case_when(
              # if it has hu(rdle) in it, we remove that and replace it with "use"
              str_detect(Effect, "hu") ~ str_replace(
                str_remove(Effect, "hu_"),
                "_", "_use_"
              ),
              # if it doesn't have hu(rdle), we know the parameter is about time
              TRUE ~ str_replace(Effect, "_", "_time_")
            )
          )
      }
      
      # next, let's finish the wrangling
      dat <- 
        dat %>% 
        # turn the Effect parameters into three separate variables
        separate(
          Effect,
          into = c("Predictor", "Use vs. Time", "Between vs. Within"),
          sep = "_"
        ) %>% 
        # renaming and selecting (only keep variables we'll need for plotting)
        select(
          Predictor,
          Outcome,
          `Use vs. Time`,
          `Between vs. Within`,
          Estimate,
          `Lower CI` = Q2.5,
          `Upper CI` = Q97.5
        )
        
      # then add those rows to the tibble we'll return
      estimates <-
        bind_rows(
          estimates,
          dat
        )
      
      # clear workspace
      rm(m)
      gc()
    }
    
    # some wrangling on final data set
    estimates <- 
      estimates %>% 
       mutate(
        # turn life into Life Satisfaction
        across(
          Predictor:Outcome,
          ~ str_replace(.x, "life", "Life Satisfaction")
        ),
        
        # factor levels to upper case
        across(
          Predictor:`Between vs. Within`,
          str_to_title
        ),
        
        # use factor still has "Used" instead of "Use" as a level
        `Use vs. Time` = str_replace(`Use vs. Time`, "Used", "Use"),
        
        # turn into factors
        across(
          Predictor:`Between vs. Within`,
          as.factor
        )
      )
    # and return
    return(estimates)
  }

# apply function
get_model_estimates(models) -> estimates
```

Alright, now let's see in which way the plot makes the most sense.
First, I need to do some wrangling on the `estimates` data frame.
Then I facet by the direction of the effect and time and use.
Not sure I like this: Four columns might be a bit much.
```{r estimates-plot1}
estimates2 <- 
  estimates %>% 
    mutate(
      # factor variable that shows the direction of effect
      Direction = if_else(Predictor %in% str_to_title(media), "Media on Well-Being", "Well-Being on Media"),
      
      # factor variable that shows which measure to facet from 
      Measure = as.factor(if_else(Predictor == "Life Satisfaction" | Outcome == "Life Satisfaction", "Life Satisfaction", "Affect")),
      
      # for which predictor/outcome the effect is visualized
      Effect = as.factor(if_else(Predictor %in% str_to_title(media), Predictor, Outcome)),
      
      # the effect on the hurdle gave us odds ratios of zero, so I reverse those to tell use odds of having used medium
      across(
        Estimate:`Upper CI`,
        ~ if_else(Direction == "Well-Being on Media", exp(-.x), .x)
      ),
      
      # the line for null effect (0 for gaussian, 1 for hurdle gamme)
      Line = if_else(Direction == "Media on Well-Being", 0, 1),
      
      # rename levels
      Effect = fct_recode(
        Effect,
        "TV" = "Tv",
        "Life satisfaction" = "Life Satisfaction"
      ),
      
      Measure = fct_recode(
        Measure,
        "Life satisfaction" = "Life Satisfaction"
      ),
      
      # reorder factor levels
      Effect = fct_relevel(
        Effect,
        c(
          "Audiobooks",
          "Magazines",
          "Books",
          "Games",
          "Films",
          "TV",
          "Music"
        )
      )
    )

ggplot(
    estimates2 %>% 
      arrange(Measure),
  aes(
    x = Estimate,
    y = Effect,
    color = Measure
  )
) +
  geom_vline(
    aes(
      xintercept = Line
    )
  ) +
  geom_pointrange(
    aes(
      xmin = `Lower CI`,
      xmax = `Upper CI`
    ),
    position = position_dodge2(.6, reverse = TRUE)
  ) +
  facet_grid(
    `Between vs. Within` ~ Direction + `Use vs. Time`,
    scales = "free_x"
  ) +
  scale_colour_manual(values=cb_palette) +
  scale_fill_manual(values = cb_palette) +
  theme(
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.line.y = element_blank(),
    strip.background.x = element_blank(),
    strip.background.y = element_blank()
  ) -> figure6.1

figure6.1
```
This looks better, in my opinion.
Shapes and colors can be tough, but I think it's easier to read than having four columns.
```{r estimates-plot2}
ggplot(
    estimates2 %>% 
      mutate(
        # ggplot weirdly shows the first level of the legend second on the graph, so I reverse level order and then reverse the legend order below with the guides command
        `Use vs. Time` = fct_relevel(
          `Use vs. Time`,
          "Time",
          "Use"
        ),
        Measure = fct_relevel(
          Measure,
          "Life satisfaction",
          "Affect"
        )
      ),
  aes(
    x = Estimate,
    y = Effect,
    color = `Use vs. Time`,
    shape = Measure,
  )
) +
  geom_vline(
    aes(
      xintercept = Line
    )
  ) +
  geom_pointrange(
    aes(
      xmin = `Lower CI`,
      xmax = `Upper CI`
    ),
    position = position_dodge2(1),
    size = 0.5
  ) +
    geom_hline(
      aes(
        yintercept = if_else(as.numeric(Effect) == 1, 0, as.numeric(Effect) - 0.5)
      ),
      color = "lightgrey",
      linetype = "dashed",
      alpha = 0.45
  ) +
  facet_grid(
    `Between vs. Within` ~ Direction,
    scales = "free_x"
  ) +
  scale_colour_manual(values=c("#000000", "#E69F00")) +
  scale_fill_manual(values = c("#000000", "#E69F00")) +
  scale_shape_manual(values=c(15, 16)) +
  guides(
    color = guide_legend(reverse = TRUE),
    shape = guide_legend(reverse = TRUE)
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.y = element_blank(),
    # axis.line.y = element_blank(),
    strip.background.x = element_blank(),
    strip.background.y = element_blank(),
    legend.position = "bottom",
  ) -> figure6.2

figure6.2

ggsave(
  filename = here("figures", "figure6.tiff"),
  plot = figure6.2,
  width = 21 * 0.9,
  height = 29.7 * 0.7,
  units = "cm",
  dpi = 300
)
```

## Interpreting the graph

Points represent the mean of the posterior distribution of the parameter.
Lines represent 95% Credible Intervals of the same posterior distribution.
The columns display reciprocal effects: On the left-hand side, coefficients are of the Gaussian models, meaning they represent an effect on the 0 to 10 well-being scale.
On the right, coefficients are of the hurdle gamma model, meaning they represent odds of using a medium at all (hurdle part) and time spent using a medium (gamma part).
The top part shows between-person effects.
The bottom part shows within-person effects.
Effects are grouped by whether or not a medium was used or how much time a person spent with a medium, and by the well-being measures, affects vs. life satisfaction.

If we take music as an example: In the top left, we see the between-person effects of music listening on affect (circle) and life satisfaction (square).
That facets also shows whether effects are of using vs. not using a medium (gold) or of time spent using a medium (black).
Across the entire sample and all waves, the model estimated that someone who listens to music, compared to someone who does not listen to music, feels somewhat worse on affect, but not on life satisfaction.
That correlation is mirrored on the top right that shows effects of affect (circle) and life satisfaction (square), across all waves, on whether someone listens to music vs. not (gold) and time listening to music (black).
So someone who feels one point better than someone else on the 0 to 10 affect measure has lower odds of listening to music compared to someone else.
Note that both facets in the top-row represent the same theoretical effects.
However, they were obtained from slightly different models, explaining their small differences.
Among those who listen to music, one hour more than someone else is only weakly related to well-being (black coefficients, left side); conversely, scoring one point higher on well-being than someone else is only weakly related to the odds of spending more time listening to music (black coefficients, right side.

The bottom left shows within-effects of listening to music: Someone who goes from not listening to music to listening to music does feel somewhat better a week later (golden circle).
At the same time, when a person listens to one hour more than they typically do, they felt slightly better, but the posterior included zero as well as negative effects (black circle).
Conversely (on the bottom right), if a person feels one point better on affect than they typically do, they do not have higher odds of listening to music a week later (golden circle).
Likewise, they don’t have higher odds of listening to more music (black circle).

## Take-aways

1. The effects we observe are on the between-level (top left): Those who use a medium also feel worse, generally. But: This only applies to use and not time: Once people use a medium, they’re not worse off than someone who spends less time with a medium.
2. Any differences happen on the less stable affect, not on life satisfaction.
3. These differences don’t seem to differ much per medium.
4. On the within-level, there isn’t much going on: Most effects are super small and include zero as a plausible effect size.
